---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---




## Loading and preprocessing the data

Show any code that is needed to

```{r}
library(tidyverse)
df_columns = cols(
  steps = col_integer(),
  date = col_date(format = ""),
  interval = col_integer()
)
df <- read_csv("activity.csv", col_types = df_columns)
```


    Load the data (i.e. read.csv())
    Process/transform the data (if necessary) into a format suitable for your analysis


## What is mean total number of steps taken per day?

The number of steps per day can be found by grouping by day and summing:
```{r steps_per_day}
steps_by_day <- df %>% group_by(date) %>% summarise(total_steps = sum(steps))
```

```{r histogram_of_steps_by_day}
ggplot(data = steps_by_day) + geom_histogram(mapping = aes(x=total_steps))
```

The mean and median daily steps can be calculated from the same frame:
```{r calculuate_daily_steps_stats}
mean_daily_steps <- mean(steps_by_day, na.rm = TRUE)
median_daily_steps <- median(steps_by_day, na.rm = TRUE)
```
The mean number of steps is `r mean_daily_steps` and the median is `r median_daily_steps`. 


## What is the average daily activity pattern?

```{r}
interval_steps <- df %>% group_by(interval) %>% summarise(mean_steps = mean(steps, na.rm = TRUE))
```

```{r}
ggplot(interval_steps) + geom_line(mapping = aes(x=interval, y=mean_steps))
```

```{r max_interval}
interval_with_most_steps <- interval_steps$interval[which.max(interval_steps$mean_steps)]
```
The interval that has the most steps (on average) is `r interval_with_most_steps`.

## Imputing missing values

The total number of NA rows in the set can be found from
```{r all_na_rows}
NA_rows <- sum(is.na(df$steps))
NA_rows
```
```{r replace_missing_intervals_with_interval_means}
df_mod <- df %>% group_by(interval) %>% mutate(steps = ifelse(is.na(steps), mean(steps, na.rm = TRUE), steps))
```

```{r}
steps_by_day_mod <- df_mod %>% group_by(date) %>% summarise(total_steps = sum(steps))
```


```{r}
ggplot(steps_by_day_mod) + geom_histogram(mapping = aes(x=total_steps))
```

```{r}

```


    Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?


## Are there differences in activity patterns between weekdays and weekends?

Are there differences in activity patterns between weekdays and weekends?

For this part the weekdays() function may be of some help here. Use the dataset with the filled-in missing values for this part.

    Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
    Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). See the README file in the GitHub repository to see an example of what this plot should look like using simulated data.





Repo

    Valid GitHub URL
    At least one commit beyond the original fork
    Valid SHA-1
    SHA-1 corresponds to a specific commit

Commit containing full submission

    Code for reading in the dataset and/or processing the data
    Histogram of the total number of steps taken each day
    Mean and median number of steps taken each day
    Time series plot of the average number of steps taken
    The 5-minute interval that, on average, contains the maximum number of steps
    Code to describe and show a strategy for imputing missing data
    Histogram of the total number of steps taken each day after missing values are imputed
    Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
    All of the R code needed to reproduce the results (numbers, plots, etc.) in the report